
\documentclass[12 pt]{paper}
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}
\usepackage{paralist}%in order to enumerate inside a paragraph
%\usepackage[hyphens]{url}
\usepackage[colorlinks=true,linkcolor=blue,anchorcolor=black,citecolor=blue,filecolor=blue,menucolor=black,runcolor=red,urlcolor=blue]{hyperref} %to get hyperlinks
\usepackage{caption}
\usepackage{subcaption}
\usepackage{csquotes}
\newbox{\bigpicturebox}%to create collage 

\usepackage[style=apa,backend=biber]{biblatex}%to cite using apa7

\usepackage{geometry}%to change page specs
\usepackage{enumitem,varwidth}%image stuff
\usepackage[svgnames]{xcolor}%image stuff, so pictures are colored
%\usepackage{tikz}%image stuff
%\usetikzlibrary{shapes.geometric} %image stuff
%\usepackage{lmodern}
\usepackage{graphicx}%to follow the template from school
\usepackage{booktabs} %to follow the template from school
 \geometry{
	a4paper,
	left=25mm,
	top=25mm,
	right=25mm,
	bottom=25mm,
}
\parindent24pt
%to follow the template from school


\graphicspath{ {./bilder/} } %where the pictures are
\addbibresource{MasterLibrary1.bib}
\title{%
Ditigization of early 1900 postcards (of Axvall)  }

\author{Sonia Lindblom \and Sicheng Yan}

\date{June 2021}

\begin{document}
\include{titlepage}

\section{Introduction}
This report of a digitization project of older postcards featuring, among others aerial photos of Axvall. -- insert dizitization in  bigger context ---. The aim of this project is to make the images available online to those interested in historical aerial photographs, for instance 
\begin{inparaenum}[i)]
	\item for geomorphology purposes \autocite[cf.][]{gomez2015}
	\item post card historical purposes
	\item history of the village
	\item military history
\end{inparaenum}
\section{Background}
Axvall is a village in Valle region, Skara Municipality, Väster Götaland county in Sweden. It was formerly a municipality itelsef, with railway station, mayor's office and other functions as well a big sanatorim, Stora Ekbergs Sanatorium. One proeminent part of Axvall's history is the housing of two military regments (frykmer1992). One of them, Skarborgs regemente trained in Axevalla hed beteween 1696 and 1913. The  other ..... 

With the extinsion of the railway and the military  


\section{Methodological work}%this has to have about 1300 words)
\subsection{Selection of the material}

The postcards were in shoeboxes without any systematization. Some of them were bound with rubberbands in bunts of 20. The conditions varied from untouched cards to others played with by kids who painted on with crayon. They were them placed in acidic free plastic boxes and grouped in categories such as hospital, housing, aerial photographs and so on, separated with laminated folders, following the recommendations of ..... 
 
The aerial photographs were of major interest since among them there were cards that were forbiden to sell due to restrictions from the Swedish Army. Since aerial photographs taken before 1950's are free to publish \autocite[][kap. 3, 3§]{lantm2018}, we decided that digitizing those images would be a good contribution for the history of Axvall. Further investigation revealed though that a photo that has been restricted before by is not included in the exception in \textcite{lantm2018}. We have search for a new assessment from Swedish Army, but have not received an answer by the end of May. To make this collection more dynamic we included then other postcards in the archive.
\subsection{Metadata}
\subsection{Image capture}
\subsection{.... platform}% Or something like webdesign

\section {Critical Analysis}


\section{Conclusions}


\newpage

%\bibliographystyle{apacite}
%\bibliography{../../../MasterLibrary.bib}
\printbibliography


\end{document}


